Scaffolder - Software for \change{Reproducible}{Manual} Genome Scaffolding.

### 2011-08-15 src/article.tex
Revise implementation

\subsection*{Input sequence data and scaffolding process} %{{{2

The input data for Scaffolder is nucleotide sequence in FASTA format file.
These nucleotide sequences can be of any length and for example may be
individual sequences, assembled contigs or contigs which have been joined to
into larger scaffolds. The case in which Scaffolder may be most useful is
using the contigs and scaffolded contigs produced from the previously
assembled set of sequencing reads, combined with additional gap filling
sequences produced by PCR or \emph{in silico} methods as outlined in the
Background. \pb

>>>>

The input data for Scaffolder is nucleotide sequence in FASTA format file.
These nucleotide sequences can be of any length and for example may be
individual \change{sequences}{reads}, assembled contigs or contigs which have
been joined to into larger scaffolds. The case in which Scaffolder may be most
useful is using the contigs and scaffolded contigs produced from the
previously assembled set of sequencing reads, combined with additional gap
filling sequences produced by PCR or \emph{in silico} methods as outlined in
the Background. \pb
